---
title: "Project.01"
author: "Pin Huang"
date: "9/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prj01 (L01)

A twin prime is a prime number that is either 2 less or 2 more than another prime number, see for details here: <https://en.wikipedia.org/wiki/Twin_prime>

* How many twin primes are bigger than one thousand but smaller than one million?

* What is the biggest twin prime you could find?

First, we creat a function to find primes.
```{r}
is_primes <- function(n) {
  p = 2:n
  i = 1
  while (p[i] <= sqrt(n)) {
    p = p[p %% p[i] !=0 | p == p[i]]
    i = i+1
  }
  p
}
```
Then, we set up a new function based on the above one to find twin primes.
```{r}
Twin_primes <- function(n) {
  if (n < 5) stop("Input value of n should be at least 5.")
  primes_less_than_N = is_primes(n)
  Twin_primes1 = primes_less_than_N[diff(primes_less_than_N) == 2]
  Twin_primes2 = Twin_primes1 + 2
  Twin_primes_set = data.frame(Twin_primes1 = Twin_primes1, Twin_primes2 = Twin_primes2)
  return(Twin_primes_set)
}
```
Hence, we can find how many pairs of twin primes between 1,000 to 1,000,000.
```{r}
nrow(Twin_primes(1000000)) - nrow(Twin_primes(1000))
```
By listing the last five pairs of twin primes, we find the biggest one which are 999959 & 999961.
```{r}
tail(Twin_primes(1000000))
```


